%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This file can be used to generate a list of symbols, abbreviations, etc.
%% as part of the front matter, BEFORE Chapter 1.
%%   For use with theses or dissertations using uwyo_thesis.sty
%%
%%   Version: 1.00
%%   Last modified: 26 August 2019
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Abbreviations, Acronyms, and Symbols}
\label{Abbreviations}  % for you to be able to refer to this appendix in the main text
\addcontentsline{toc}{chapter}{Abbreviations, Acronyms, and Symbols} % make this show up in TOC


% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
{ % begin special environment for abbreviations  -- modify only with great care!

 \setlength{\parindent}{0pt}

%%%%% commands just for this file %%%%%%%%%%%%%%%%%%%%%%%
 \newcommand{\abbrltr}[1]{% command for letter section
   \bigskip
   \framebox{\textbf{#1}}
   \medskip
 }
 \newlength{\abbrwidth}
 \newlength{\abbrdef}
 \setlength{\abbrwidth}{0.9in}  % adjust for longest abbreviation
 \setlength{\abbrdef}{\textwidth}
 \addtolength{\abbrdef}{-\abbrwidth}
 \newcommand{\abbr}[2]{% command for an entry
   \begin{tabular}{p{\abbrwidth}p{\abbrdef}}
     \textbf{#1} & {#2}
   \end{tabular}

 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
%% start appendix text %%
%%%%%%%%%%%%%%%%%%%%%%%%

This is a partial list of abbreviations, acronyms, and symbols used in the
text, provided in the hope that it will be helpful to some readers.

\abbrltr{Symbols}

\abbr{$\hat{}$}{Refers to predictions.}

\abbr{$p_{\cap}$}{Threshold for the computed joint probability.}

\abbrltr{Greek Letters}

\abbr{$\mu$}{Mean prediction.}

\abbr{$\sigma$}{Standard deviation of prediction.}

\abbrltr{A}

\abbr{AI}{Artificial Intelligence.}

\abbr{AS}{Algorithm selection.}

\abbr{ASLib}{Algorithm selection library.}

\abbr{ASP}{Answer set programming.}

\abbr{AutoML}{Automated machine learning.}

% \abbrltr{B}

\abbrltr{C}

\abbr{CASH}{Combined algorithm selection and hyperparameter optimization.}

\abbr{CDCL}{Conflict-Driven Clause Learning algorithm.}

\abbr{CNF}{Conjunctive normal form.}

\abbr{COP}{Constraint optimization problem.}

\abbr{CP}{Constraint programming.}

\abbr{CSHS}{Cost-sensitive hierarchical clustering.}

\abbr{CSP}{Constraint satisfaction problem.}

\abbrltr{D}

\abbr{DPLL}{Davis-Putnam-Loveland-Logemann algorithm.}

% \abbrltr{E}

\abbrltr{F}

\abbr{FPGA}{Field-programmable gate array.}

\abbrltr{G}

\abbr{GPU}{Graphical processing unit.}

\abbrltr{H}

\abbr{HPO}{Hyperparameter optimization.}

\abbrltr{I}

\abbr{IP}{Integer programming.}

\abbr{ISA}{Instance-specific ASPEED}

\abbr{ISAC}{Instance-specific algorithm configuration.}

% \abbrltr{J}

\abbrltr{K}

\abbr{KL}{Kullback–Leibler (KL) divergence.}

\abbr{KNN}{K-nearest neighbors.}

\abbrltr{L}

\abbr{LLAMA}{Leveraging learning to automatically manage algorithms.}

\abbrltr{M}

\abbr{MAB}{Multi-armed bandit.}

\abbr{MCP}{Misclassification penalty.}

\abbr{MIP}{Mixed integer programming.}

\abbr{ML}{Machine learning.}

\abbr{MPE}{Most probable explanations}

\abbrltr{N}

\abbr{NP}{Nondeterministic polynomial time.}

\abbr{NFL}{No free lunch theorem.}
% \abbrltr{O}

\abbrltr{P}

\abbr{PAR2}{Penalized average runtime with factor of 2.}

\abbr{PAR10}{Penalized average runtime with factor of 10.}

\abbr{PDDL}{Planning domain definition language.}

\abbr{PPP}{Plain parallel portfolio.}

\abbrltr{Q}

\abbr{QBF}{Quantified boolean formulas.}


\abbrltr{R}

\abbr{RF}{Random forests.}

\abbr{RFJ}{Randomforests model with Jackknife uncertainty method.}

\abbr{RI}{Ranger model with Infinitesimal Jackknife uncertainty method.}

\abbr{RJ}{Ranger model with Jackknife uncertainty method.}

\abbrltr{S}

\abbr{SAT}{Boolean satisfiability problem.}

\abbr{SBS}{Single best solver.}

\abbr{SHAP}{SHapley Additive exPlanations.}

\abbr{SNNAP}{Solver-based nearest
neighbor for algorithm portfolios.}

\abbr{SMT}{Satisfiability modulo theories.}

\abbr{SVR}{Support vector regression.}
\abbrltr{T}

\abbr{TSP}{Traveling salesman problem.}

% \abbrltr{U}

\abbrltr{V}

\abbr{VBS}{Virtual best solver.}

% \abbrltr{W}

% \abbrltr{X}

% \abbrltr{Y}

% \abbrltr{Z}

% % % % % % % % % % % % % % % % % % % % % % % % %
} % end environment for zero \parindent  -- do not remove this curly brace

%\mycleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%
%%% end appendix text %%%
%%%%%%%%%%%%%%%%%%%%%%%%


